### 2017-07-01 paper/lexicographic-programs.tex
started writing the section on algorithm

We now have all the ingredients needed to define the notion of LexRSM maps for probabilistic programs.

\begin{definition}[Lexicographic Ranking Supermartingale Map]
Let $\eps>0$. An $n$-dimensional \emph{lexicographic $\eps$-ranking supermartingale map} ($\eps$-LexRSM map) for a program $\program$ supported by an invariant map $\inv$ is an $n$-dimensional measurable map $\vec{\lem}=(\lem_1,\dots,\lem_n)$ for $\program$ such that for each configuration $(\loc,\vec{x})$ where $\loc\neq \locterm$ and $\vec{x}\in \inv(\loc)$ the following conditions are satisfied:
 \begin{compactitem}
 	%\item For all $(\loc,\vec{x})\in \locs\times\Rset^{|\pvars|}$ it holds
 	%\item For all  it holds 
 	\item
 	for all $1\leq j \leq n$, $\lem_j(\loc,\vec{x})\geq 0$; and
 	\item 
 	for each generalized transition $\tilde{\tau}$ outgoing from $\loc$ there 
 	exists $1\leq j 
 	\leq$ n such that
 	\begin{compactitem}
 	\item
 	$\tilde{\tau}$ is $\eps$-ranked by $\lem_j$ from $(\loc,\vec{x})$
 	\item
 	for all $1\leq j'<j$ we have that $\tilde{\tau}$ is unaffected by 
 	$\lem_{j'}$ from $(\loc,\vec{x})$.
 	\end{compactitem}
 \end{compactitem}
If additionally $\lem$ is a linear expression map, then we call it a linear $\eps$-LexRSM map ($\eps$-LinLexRSM).
\end{definition}

>>>>

We now have all the ingredients needed to define the notion of LexRSM maps for probabilistic programs. For notational convenience, we extend the function $\guards$ (which assigns guards to deterministic transitions) to the set of all generalized transition: for a generalized transition $\tau'$ which is not a standard transition outgoing from deterministic location, we put $\guards(\tau')=0\leq 0 \equiv \mathit{true}$.

\begin{definition}[Lexicographic Ranking Supermartingale Map]
Let $\eps>0$. An $n$-dimensional \emph{lexicographic $\eps$-ranking supermartingale map} ($\eps$-LexRSM map) for a program $\program$ supported by an invariant map $\inv$ is an $n$-dimensional measurable map $\vec{\lem}=(\lem_1,\dots,\lem_n)$ for $\program$ such that for each configuration $(\loc,\vec{x})$ where $\loc\neq \locterm$ and $\vec{x}\in \inv(\loc)$ the following conditions are satisfied:
 \begin{compactitem}
 	%\item For all $(\loc,\vec{x})\in \locs\times\Rset^{|\pvars|}$ it holds
 	%\item For all  it holds 
 	\item
 	for all $1\leq j \leq n$, $\lem_j(\loc,\vec{x})\geq 0$; and
 	\item 
 	for each generalized transition $\tilde{\tau}$ outgoing from $\loc$ such that $\vec{x}\models\guards(\tilde\tau)$ there 
 	exists $1\leq j 
 	\leq$ n such that
 	\begin{compactitem}
 	\item
 	$\tilde{\tau}$ is $\eps$-ranked by $\lem_j$ from $(\loc,\vec{x})$
 	\item
 	for all $1\leq j'<j$ we have that $\tilde{\tau}$ is unaffected by 
 	$\lem_{j'}$ from $(\loc,\vec{x})$.
 	\end{compactitem}
 \end{compactitem}
If additionally $\lem$ is a linear expression map, then we call it a linear $\eps$-LexRSM map ($\eps$-LinLexRSM).
\end{definition}
